Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-08-25 paper/ms.tex
prada

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{concentration_bolshoi.pdf}
  \includegraphics[width=0.49\textwidth]{concentration_bolshoi_corrected.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Mass-concentration relationship for the three different
  methods on the Bolshoi data using only relaxed halos.
  The lines correspond to the median concentration values in each mass
  bin.  
  The shaded region presents 10 and 90 per cent spread. 
  The three methods have a similar spread but for clarity we only show
  the spread for the concentrations estimated using the new method.   
  The dotted line corresponds to fits reported by \citep{Prada2012}.
  The left panel shows the raw results coming from each algorithm. 
  The right panel introduces a correction on the velocity and
  integrated mass results following the results of the downsampling
  experiments presented in Figure 
  \ref{fig:downsampling}.
  \label{fig:concentration}} 
\end{figure*}

@@

How do these results impact the most recent mass-concentration estimates? 
\cite{Ludlow2016} and \cite{Klypin2016} estimated the mass-concentration
relation over different suites of cosmological N-body simulations using the
density and velocity methods, respectively. 
Both used halos with at least $5\times 10^{3}$ particles.
This imposes a lower halo mass limit of $\sim 10^{12}$\hMsun (Figure 8
in \cite{Ludlow2016}, Figure 17 in \cite{Klypin2016}) to have robust
estimates. 
This means that their results for individual halos should not be
affected by the bias we report here.
However, this also leaves open the question about what other methods
can robustly say about the flattening we report below $10^{12}$\Msun
using the new method.

@@

 We acknowledge financial support from Uniandes
 and Universidad de Antioquia. 
 We thank Tom\'as Verdugo, Stefan Gottloeber and Nelson  Padilla for
their feedback.
We thank the anonymous referee for comments that improved
the presentation of these results.

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{concentration_bolshoi.pdf}
  \includegraphics[width=0.49\textwidth]{concentration_bolshoi_corrected.pdf}
\end{center}
\vspace{-0.5cm}
\caption{Mass-concentration relationship for the three different
  methods on the Bolshoi data using only relaxed halos.
  The lines correspond to the median concentration values in each mass
  bin.  
  The shaded region presents 10 and 90 per cent spread. 
  The three methods have a similar spread but for clarity we only show
  the spread for the new method.   
  The dotted line corresponds to fits reported by \citep{Prada2012}.
  The left panel shows the raw results coming from each algorithm. 
  The right panel introduces a correction on the velocity and
  integrated mass results following the results of the downsampling
  experiments presented in Figure 
  \ref{fig:downsampling}.
  \label{fig:concentration}} 
\end{figure*}

@@

How do these results impact the most recent mass-concentration estimates? 
\cite{Ludlow2016} and \cite{Klypin2016} estimated the mass-concentration
relation over different suites of cosmological N-body simulations using the
density and velocity methods, respectively. 
Both used halos with at least $5\times 10^{3}$ particles.
This imposes a lower halo mass limit of $\sim 10^{12}$\hMsun (Figure 8
in \cite{Ludlow2016}, Figure 17 in \cite{Klypin2016}) to have robust
estimates. 
This means that their results for individual halos should not be
affected by the bias we report here.
This also leaves open the question about what other methods
can robustly say about the flattening we report below $10^{12}$\Msun
using the new method. 
However, there are other results at lower masses and higher redshifts
\citep[i.e.][]{Prada2012} that should be reconfirmed using higher resolution
simulations as they use halos with only $500$ particles.

@@

 We acknowledge financial support from Uniandes
 and Universidad de Antioquia. 
 We thank Tom\'as Verdugo, Stefan Gottloeber and Nelson  Padilla for
their feedback.
We thank the anonymous referees for comments that improved
the presentation of these results.
